Instructions for \confname{} Proceedings

### 2019-05-10 papers/EMNLP2019/analysis.tex
middle of analysis results

\subsection{Beyond synonymy and hypernymy: cross-classification}

\gbt{@Sina, for this section/my analysis, I'd need csvs (or some code that builds dataframes) containing the following (see commented text):}

  % \begin{enumerate}
  % \item Dataframe for images: for each image,
  %   \begin{itemize}
  %   \item top -- top name
  %   \item \% top
  %   \item SN -- snodgrass agreement
  %   \item =VG
  %   \item dictionary or similar with names and counts
  %   \end{itemize}
  % \item Dataframe for name variants: for each variant pair,
  %   \begin{itemize}
  %   \item top name
  %   \item variant
  %   \item frequency of the pair
  %   \item domain of top
  %   \item domain of variant (one of ours or ``OTHER'' if not in any of them?)
  %   \item relationship in wordnet, one of: synonymy, hyponymy, co-hyponymy, other, not in wordnet (agree? the latter means ``one of the elements not in wordnet'')
  %   \end{itemize}
  % \end{enumerate}

Some (interesting, somewhat cherry-picked) word pairs were WordNet does not find any relation (excluded in the above analysis):

\begin{itemize}
\item lettuce -- salad
\item fruit -- food
\item man -- catcher
\item bowl --chili
\item bowl -- diner \gbt{spelling mistake? should be dinner?} 
\item burger -- meat
\item statue -- animal (image shows statue of an animal)
\item bottle -- alcohol
\item donut --desert \gbt{spelling mistake? should be dessert?} 
\item zebra -- stripes
\item oven -- grill
\end{itemize}

@@

>>>>

\subsection{Crossclassified}

Table

\begin{table*}
  \label{tab:crossclass}
\small
\begin{tabular}{lrl|lrl}
  \toprule
    \multicolumn{3}{c}{same object (217; 31\%)} & \multicolumn{3}{c}{not same object (483; 69\%)}\\
\midrule
co-hyponyms &          104  & horse-donkey, truck-jeep, castle-church & adjacent   &          167 & building-clock, cat-pole, bed-chair\\
overlapping &           69  & skater-boy, cat-toy, horse-statue & supports.1 &          122 & couch-pillow, bowl-fruit, person-dress\\
hypernym.1  &           18  & hat-beanie, jacket-tuxedo, building-hut & part.2     &102& plane-wings, pizza-cheese\\
hypernym.2  &           16  & donut-pastry, train-vehicle, van-automobile & supports.2 &           64 & shirt-child, donut-plate, carpet-floor\\
other       &            8  & sandwich-meal, plane-plain, umbrella-tent & part.1     &           20 & wheel-moped, sink-counter, bread-sub\\
	    & 		    & & other      &           10 & plane-flight, horse-wood\\
\bottomrule
\end{tabular}
\caption{Relations between words or objects when the variants refer to the same object (left) or not (right).}
\end{table*}

@@

% \begin{itemize}
% \item lettuce -- salad
% \item fruit -- food
% \item man -- catcher
% \item bowl --chili
% \item bowl -- diner \gbt{spelling mistake? should be dinner?} 
% \item burger -- meat
% \item statue -- animal (image shows statue of an animal)
% \item bottle -- alcohol
% \item donut --desert \gbt{spelling mistake? should be dessert?} 
% \item zebra -- stripes
% \item oven -- grill
% \end{itemize}
